Eagle: Making multiple-locus association mapping on a genome-wide scale routine

### 2018-08-02 paper.tex
3Aug refinement v1

\subsection{Stability Selection}
Stability selection is a subsampling strategy with a wide range of applications.  In the context of regularisation methods, it is a way of estimating, 
empirically, the significance of the effects. Compared to permutation, the amount of computation is significantly less.  
Analyses are based on only a fraction of the data  and the regularisation parameter need not be optimised.  
To perform stability selection, we did the following.  
For LMM-Lasso and glmnet, the regularisation parameter was fixed to a "suitable" value. This was done  
via a preliminary analysis of the data where we adjusted the regularisation parameter  to yield
between 20 to 30 SNPs with non-zero effect sizes.  Here, the number of non-zero effects is rather arbitrary and any reasonable 
number of non-zero effects would suffice. 
 We then repeatedly subsampled, without replacement, the data. As recommended \cite{meinshausen2010stability}, we drew 100 subsamples of size $n/2$ from the data. Each subsample was analysed with LMM-Lasso and glmnet, with their regularisation parameters fixed. 
A (probability) estimate of the statistical significance of a SNP effect is obtained by counting the 
number of times the SNP had a non-zero effect size over all the replicates divided by the number of replicates (which was 100).

>>>>

\subsection{Stability Selection}
Stability selection is a subsampling strategy with a range of applications, including the estimation of significance in regression models where 
the number of parameters ($p$) is much larger than the number of samples ($n$). We chose stability selection over permutation and other 
sampling procedures because of its low computational cost. 
Stability selection proceeds as follows. For LMM-Lasso and 
glmnet, we begin by performing a preliminary analysis of the data where  we set the  regularisation parameter to a value that yields 20 to 30 non-zero SNP effects. This was based on the number of SNP-trait associations we thought was realistic for the data. Fortunately, the significance estimates from 
stablity selection are robust (ref) so any reasonable number here would suffice.

 selection is a subsampling strategy with a wide range of applications,  one of which is estimating the 
statistical significance of effects in a regression model. Stability selection only requires analyses to take place on a fraction of the data. 
Also, for these analyses, there is no need to find the entire solution path for the regularisation method. Instead, the regularisation method 
is run at a fixed value of the regularisation parameter. This gives stability selection a much lower computational cost than other 
sampling approaches such as permutation and multi-sampling.

For the analysis of the simulated data, stability selection for LMM-Lasso and glmnet proceeds as follows. 
We began by finding the value of the regularisation parameter 
that gave 20 to 30 SNPs with non-zero effects.  This number was based on our a priori knowledge of the expected 
number of SNPs in association with the (simulated) trait. Obviously, this is unknown when analysing real data.

Stability selection for LMM-Lasso and glmnet was performed as follows. We began by finding the value of the regularisation parameter 
that gave 20 to 30 SNPs with non-zero effects. This number was based on our a priori belief of the number of SNPs in association with the trait.

 of 20 to 30 was based upon the number of SNP-trait associations we thought could 
be found from the data.

A preliminary analysis of the data was conducted to find the value 
of the regularisation parameter that yields 20 to 30 SNPs with non-zero effect sizes.

To perform stability selection, we did the following.  
We began by fixing the regularisation parameter  of LMM-Lasso and glment to a "suitable" value. Through preliminary analyses of the data, 
we were able to adjust the regularisation parameter to yield 20 to 30 SNPs with non-zero effect sizes. This number of 20 to 30 was based on 
the number of findings we were expecting from the analysis of the simulated data. Obviously, in practice, this is unknown. However,  the estimates 
from stability selection are  robust (ref) so fixing the regularisation parameter to return any reasonable number of non-zero effect sizes would suffice. 
 We repeatedly subsampled, without replacement, the data. We drew 
 100 subsamples of size $n/2$ from the data \cite{meinshausen2010stability}. Each subsample was analysed with LMM-Lasso and glmnet. 
 The analyses were performed with the regularisation parameter fixed to the value found from the preliminary analysis.
A (probability) estimate of the statistical significance of a SNP effect is obtained by counting the 
number of times the SNP had a non-zero effect size over all the replicates divided by the number of replicates (which was 100).
